Providing better confidentiality and authentication on the Internet using Namecoin and MinimaLT

### 2014-01-05 paper.tex
alright, time for a first draft :)

\newpage
\section{Transport security}

Now that we have a good long-term identity key distribution strategy, we are going to introduce a new transport-layer security protocol that provides safer and faster encrypted connections.
\subsection{MinimaLT}
MinimaLT\cite{MinimaLT} is a new\footnote{Paper published in Mai 2013} that looks really promising.
protocol that presents some of the interesting features we want. It was initially designed to secure network connections between computers running the secure operating system \emph{Ethos}. In the following sections we are going to compare it with TLS/TCP.\footnote{We are however not going to go over the whole specification of the protocol.} 
MinimaLT is implemented on top of UDP to be compatible with the current Internet infrastructure and end-systems.

@@

@@

\begin{lstlisting}[language=json,firstnumber=1]
{
    "minimaLT": {
        "eph_key": ephemeral key used for sending encrypted data on first RTT.
    }
}

@@

//\balance

@@

This mashup wouldn't have been possible without the underlying pieces, namely Namecoin and MinimaLT.

Most of the Namecoin research is based on Greg Slepak's paper\cite{okTurtles} \emph{OkTurtles + DNSNMC}. 
\bibliographystyle{abbrv}
\bibliography{bibliography}

>>>>

\section{Transport security}

Now that we have a good long-term identity key distribution strategy, we are going to introduce a new transport-layer security protocol that provides safer and faster encrypted connections.
\subsection{MinimaLT}
MinimaLT\cite{MinimaLT} is a new\footnote{Paper published in May 2013} protocol that looks really promising.
It presents some of the interesting features we want. It was initially designed to secure network connections between computers running the secure operating system \emph{Ethos}. In the following sections we are going to compare it with TLS/TCP.\footnote{We are however not going to go over the whole specification of the protocol.} 
MinimaLT is implemented on top of UDP to be compatible with the current Internet infrastructure and end-systems.

@@

\newpage

@@

\begin{lstlisting}[language=json,firstnumber=1]
{
    "minimaLT": {
        "eph_key": ephemeral key used for sending encrypted data on first RTT.
    }
}
\end{lstlisting}

@@

\balance

@@

Still to do 
\bibliographystyle{abbrv}
\bibliography{bibliography}
